---
title: "README"
author: "David Kaiser"
date: "29 8 2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Carbonate System - relationships between parameters

Find an interactive `shiny` app that displays the relationship between different parameters of the carbonate system [**here**](https://davidatlarge.shinyapps.io/shiny_carb_plot/?_ga=2.134770553.964002575.1598730102-1166230829.1598207332). 
The concentrations of CO~2~ and CO~3~^2-^ on the axes are in µmol kg^-1^. The other parameters are calculated using `seacarb::carb()`. The values on the contours are in mol kg^-1^! The plot is inspired by an old [presentation by Andrew Dickson](https://www.youtube.com/watch?v=dR917nXLEHU).

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
co2_data <- expand.grid(
  co2 = seq(from = 0, to = 100, length.out = 101),
  co3 = seq(from = 0, to = 300, length.out = 101)
)

carb.data <- cbind(co2_data,
        seacarb::carb(
          flag = 3,
          var1 = co2_data$co2 / 1000000,
          var2 = co2_data$co3 / 1000000,
          S = 35,
          T = 25,
          P = 0,
          Patm = 1,
          Pt = 0,
          Sit = 0,
          k1k2 = "x",
          kf = "x",
          ks = "d",
          pHscale = "T"
        ) %>%
          select(-c(flag, S, T, Patm, P, CO2, CO3)) 
  ) %>%
    #.[,order(colnames(.))] %>%
    na_if("-Inf") %>% 
    na_if("Inf") # geom_label_contour does not handle Inf

```

```{r plot, echo=FALSE, message=FALSE, warning=FALSE}

    carb.data %>%
    ggplot(aes(x = co2, y = co3, z = ALK, na), na.rm = TRUE) +
    geom_contour(size = 1) +
    metR::geom_label_contour() +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_light() +
    theme(text = element_text(size = 20))


```

```{r table, echo=FALSE}

# inputPanel({
#   sliderInput(inputId = "n_row", label = "Rows to display", width = "5cm",
#               min = 0, max = 10200, value = c(0,10), step = 5)
# })
# 
# renderTable({
#   carb.data()[input$n_row[1]:input$n_row[2],]
# })

head(carb.data)

```


