---
title: "Carb"
author: "David Kaiser"
date: "23 8 2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Carbonate System - relationships between parameters

This `shiny` app displays the relationship between different parameters of the carbonate system. 
The concentrations of CO~2~ and CO~3~^2-^ on the axes are in $\mu$mol kg^-1^. The other parameters are calculated using `seacarb::carb()`. The plot is inspired by an old [presentation by Andrew Dickson](https://www.youtube.com/watch?v=dR917nXLEHU). I will make the x and y parameters selectable later.

```{r data, echo=FALSE}

inputPanel(
  numericInput("temp", label = "temperature value [°C]", value = 25),
  numericInput("sal", label = "salinity value", value = 35),
  numericInput("pressure", label = "hydrostatic pressure [bar]", value = 0),
  numericInput("Patm", label = "atmospheric pressure [atm]", value = 1)
)

co2_data <- expand.grid(
  co2 = seq(from = 0, to = 100, length.out = 101),
  co3 = seq(from = 0, to = 300, length.out = 101)
)

carb.data <- reactive({
  cbind(co2_data,
        seacarb::carb(
          flag = 3,
          var1 = co2_data$co2 / 1000000,
          var2 = co2_data$co3 / 1000000,
          S = input$sal,
          T = input$temp,
          P = input$pressure,
          Patm = input$Patm,
          Pt = 0,
          Sit = 0,
          k1k2 = "x",
          kf = "x",
          ks = "d",
          pHscale = "T"
        ) %>%
          select(-c(flag, S, T, Patm, P, CO2, CO3)) 
  ) %>%
    #.[,order(colnames(.))] %>%
    na_if("-Inf") %>% 
    na_if("Inf") # geom_label_contour does not handle Inf
})


```

```{r plot, echo=FALSE}

inputPanel(
  selectInput(inputId = "parameter", 
              label = "dependent parameter",
              choices = c("ALK", "DIC", "fCO2", "fCO2insitu", "fCO2pot", 
                          "HCO3", "OmegaAragonite", "OmegaCalcite", "pCO2", "pCO2insitu", "pCO2pot", "pH"))
)

renderPlot({
  carb.data() %>%
    ggplot(aes_string(x = "co2", y = "co3", z = input$parameter)) +
    geom_contour(size = 1) +
    metR::geom_label_contour() +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_light() +
    theme(text = element_text(size = 20))
})

```

```{r table, echo=FALSE}

inputPanel({
  sliderInput(inputId = "n_row", label = "Rows to display", width = "5cm",
              min = 0, max = 10200, value = c(0,10), step = 5)
})

renderTable({
  carb.data()[input$n_row[1]:input$n_row[2],]
})

```


